R Notebook

### 2020-01-25 src/comb-maxent.Rmd
moving forward... back to where i was

@@

```{r avg asc layers cloglog}
mthna <- "aug" #change me
depthlayers <- read.csv(paste0("../output/maxent/predictions/com-split/", mthna, "/cloglog_asclayerbydepth.csv"), header = TRUE)
p <- list.dirs("../output/maxent/models/test-comb", recursive = FALSE, full.names = FALSE)
modlist <- p[ grepl(mthna, p) ]
print(length(modlist)) #need this to modify code below
print(modlist) #need this to modify code below

for (x in 1:nrow(depthlayers)){
  asclay <- depthlayers[x, ]
  asclay <- asclay[!is.na(asclay)]
  asclay <- as.data.frame(rbind(asclay))
  asclay$V1 <- as.character(asclay$V1) #v1 just a number
  asclay$V2 <- as.character(asclay$V2) #v2 corresponds to depth
  asclay$V3 <- as.character(asclay$V3) #yr 1
  asclay$V4 <- as.character(asclay$V4) #yr 2
  asclay$V5 <- as.character(asclay$V5) #yr 3
  asclay$V6 <- as.character(asclay$V6) #yr 4
  asclay$V7 <- as.character(asclay$V7)
  asclay$V8 <- as.character(asclay$V8) #yr 6
  asclay$V9 <- as.character(asclay$V9)
  asclay$V10 <- as.character(asclay$V10) #yr 8
  asclay$V11 <- as.character(asclay$V11)
  asclay$V12 <- as.character(asclay$V12) #yr 10
  # asclay$V13 <- as.character(asclay$V13)
  # asclay$V14 <- as.character(asclay$V14) #yr 12
  # asclay$V15 <- as.character(asclay$V15)
  # asclay$V16 <- as.character(asclay$V16) #yr 14
  # asclay$V17<- as.character(asclay$V17)
  #asclay$V18 <- as.character(asclay$V18) #yr 16
  #asclay$V19 <- as.character(asclay$V19) #yr 17

@@

  # asc1998 <- raster(asclay$V3)
  # asc1999 <- raster(asclay$V4)
  # asc2000 <- raster(asclay$V5)
  # asc2001 <- raster(asclay$V6)
  # asc2002 <- raster(asclay$V7)
  # asc2003 <- raster(asclay$V8)
  asc2004 <- raster(asclay$V3)
  asc2005 <- raster(asclay$V4)
  asc2006 <- raster(asclay$V5)
  asc2007 <- raster(asclay$V6)
  asc2008 <- raster(asclay$V7)
 # asc2009 <- raster(asclay$V14)
  asc2010 <- raster(asclay$V8)
  asc2011 <- raster(asclay$V9)
  asc2012 <- raster(asclay$V10)
  asc2013 <- raster(asclay$V11)
  asc2014 <- raster(asclay$V12)
  # asc2015 <- raster(asclay$V20)

  stkasc <- stack(asc2004, asc2005, asc2006, asc2007, asc2008, asc2010, asc2011, asc2012, asc2013, asc2014) #, asc2015)   asc1998, asc1999, asc2000, asc2001, asc2002, asc2003, asc2009

@@

file.rename(paste0("../output/maxent/predictions/com-split/", mthna, "/avg_cloglog_000120.asc"), paste0("../output/maxent/predictions/", mthna, "/avg_cloglog_120.asc"))
file.rename(paste0("../output/maxent/predictions/com-split/", mthna, "/avg_cloglog_000120.png"), paste0("../output/maxent/predictions/", mthna, "/avg_cloglog_120.png"))
file.rename(paste0("../output/maxent/predictions/com-split/", mthna, "/avg_cloglog_041.18.asc"), paste0("../output/maxent/predictions/", mthna, "/avg_cloglog_41.18.asc"))
file.rename(paste0("../output/maxent/predictions/com-split/", mthna, "/avg_cloglog_041.18.png"), paste0("../output/maxent/predictions/", mthna, "/avg_cloglog_41.18.png"))
}
```

@@

```{r}
outsidemcp <- shapefile("../data/env/landp/mcpout.shp") #made in arcgis
wgsraster <- raster("../output/maxent/predictions/com-split/apr/cloglog_1998_04_0.50576.asc") #just chosen randomly to act as dummy file
crs(wgsraster) <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0 "
outsidemcp <- spTransform(outsidemcp, crs(wgsraster))

clogasc_list <- list.files(paste0("../output/maxent/predictions/com-split/dec"), pattern = "^avg_cloglog_.*.asc", full.names = TRUE) #just choose a random month to calculate cells
cumst <- data.frame(0, 0)
colnames(cumst) <- c("depth", "no_cells")
for (cum in 1:length(clogasc_list)){
  cumasc <- raster(clogasc_list[6])
  ascname <- names(cumasc)
  cumst[cum, 1] <- str_sub(ascname, 13)
  cumasc2 <- raster::mask(cumasc, outsidemcp, inverse = TRUE)
  ccnt <- freq(cumasc2, useNA='no')
  ccnt <- sum(ccnt[ ,2])
  cumst[cum, 2] <- ccnt
}

@@

```{r bin probabilities}
outsidemcp <- shapefile("../data/env/landp/mcpout.shp") #made in arcgis
mthord <- c("dec") #"mar", "apr", "may", "jun", "jul", "aug", "sep", "oct", "nov",

for (m in 1:length(mthord)){
  mth <- mthord[m]
  clogasc_list <- list.files(paste0("../output/maxent/predictions/", mth), pattern = "^avg_cloglog.*.asc", full.names = TRUE)

@@

  for (cum in 1:length(clogasc_list)){
    cumasc <- raster(clogasc_list[cum])
    ascname <- names(cumasc)
    cumasc <- mask(cumasc, outsidemcp, inverse = TRUE)
    probbin <- calc(cumasc, fun = binprob) #creates raster layer with cell values based on the binprob function
    writeRaster(probbin, paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_binned_1_avgprob_", ascname, ".asc"), overwrite = TRUE)
    plot(probbin, png(paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_binned_1_avgprob_", ascname, ".png")), overwrite = TRUE)
    dev.off() # stops automatic saving of the plot to a png
  }

@@

  for (cum in 1:length(clogasc_list)){
    cumasc <- raster(clogasc_list[cum])
    ascname <- names(cumasc)
    cumasc <- mask(cumasc, outsidemcp, inverse = TRUE)
    probbin <- calc(cumasc, fun = binprob) #creates raster layer with cell values based on the binprob function
    writeRaster(probbin, paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_binned_2_avgprob_", ascname, ".asc"), overwrite = TRUE)
    plot(probbin, png(paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_binned_2_avgprob_", ascname, ".png")), overwrite = TRUE)
    dev.off() # stops automatic saving of the plot to a png
  }

@@

  for (cum in 1:length(clogasc_list)){
    cumasc <- raster(clogasc_list[cum])
    ascname <- names(cumasc)
    cumasc <- mask(cumasc, outsidemcp, inverse = TRUE)
    probbin <- calc(cumasc, fun = binprob) #creates raster layer with cell values based on the binprob function
    writeRaster(probbin, paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_binned_3_avgprob_", ascname, ".asc"), overwrite = TRUE)
    plot(probbin, png(paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_binned_3_avgprob_", ascname, ".png")), overwrite = TRUE)
    dev.off() # stops automatic saving of the plot to a png
  }

@@

  for (cum in 1:length(clogasc_list)){
    cumasc <- raster(clogasc_list[cum])
    ascname <- names(cumasc)
    cumasc <- mask(cumasc, outsidemcp, inverse = TRUE)
    probbin <- calc(cumasc, fun = binprob) #creates raster layer with cell values based on the binprob function
    writeRaster(probbin, paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_binned_4_avgprob_", ascname, ".asc"), overwrite = TRUE)
    plot(probbin, png(paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_binned_4_avgprob_", ascname, ".png")), overwrite = TRUE)
    dev.off() # stops automatic saving of the plot to a png
  }

@@

  for (cum in 1:length(clogasc_list)){
    cumasc <- raster(clogasc_list[cum])
    ascname <- names(cumasc)
    cumasc <- mask(cumasc, outsidemcp, inverse = TRUE)
    probbin <- calc(cumasc, fun = binprob) #creates raster layer with cell values based on the binprob function
    writeRaster(probbin, paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_binned_5_avgprob_", ascname, ".asc"), overwrite = TRUE)
    plot(probbin, png(paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_binned_5_avgprob_", ascname, ".png")), overwrite = TRUE)
    dev.off() # stops automatic saving of the plot to a png
  }

@@

  for (cum in 1:length(clogasc_list)){
    cumasc <- raster(clogasc_list[cum])
    ascname <- names(cumasc)
    cumasc <- mask(cumasc, outsidemcp, inverse = TRUE)
    probbin <- calc(cumasc, fun = binprob) #creates raster layer with cell values based on the binprob function
    writeRaster(probbin, paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_binned_6_avgprob_", ascname, ".asc"), overwrite = TRUE)
    plot(probbin, png(paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_binned_6_avgprob_", ascname, ".png")), overwrite = TRUE)
    dev.off() # stops automatic saving of the plot to a png
  }

@@

  for (cum in 1:length(clogasc_list)){
    cumasc <- raster(clogasc_list[cum])
    ascname <- names(cumasc)
    cumasc <- mask(cumasc, outsidemcp, inverse = TRUE)
    probbin <- calc(cumasc, fun = binprob) #creates raster layer with cell values based on the binprob function
    writeRaster(probbin, paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_binned_7_avgprob_", ascname, ".asc"), overwrite = TRUE)
    plot(probbin, png(paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_binned_7_avgprob_", ascname, ".png")), overwrite = TRUE)
    dev.off() # stops automatic saving of the plot to a png
  }

@@

  for (cum in 1:length(clogasc_list)){
    cumasc <- raster(clogasc_list[cum])
    ascname <- names(cumasc)
    cumasc <- mask(cumasc, outsidemcp, inverse = TRUE)
    probbin <- calc(cumasc, fun = binprob) #creates raster layer with cell values based on the binprob function
    writeRaster(probbin, paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_binned_8_avgprob_", ascname, ".asc"), overwrite = TRUE)
    plot(probbin, png(paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_binned_8_avgprob_", ascname, ".png")), overwrite = TRUE)
    dev.off() # stops automatic saving of the plot to a png
  }

@@

  for (cum in 1:length(clogasc_list)){
    cumasc <- raster(clogasc_list[cum])
    ascname <- names(cumasc)
    cumasc <- mask(cumasc, outsidemcp, inverse = TRUE)
    probbin <- calc(cumasc, fun = binprob) #creates raster layer with cell values based on the binprob function
    writeRaster(probbin, paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_binned_9_avgprob_", ascname, ".asc"), overwrite = TRUE)
    plot(probbin, png(paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_binned_9_avgprob_", ascname, ".png")), overwrite = TRUE)
    dev.off() # stops automatic saving of the plot to a png
  }

@@

  for (cum in 1:length(clogasc_list)){
    cumasc <- raster(clogasc_list[cum])
    ascname <- names(cumasc)
    cumasc <- mask(cumasc, outsidemcp, inverse = TRUE)
    probbin <- calc(cumasc, fun = binprob) #creates raster layer with cell values based on the binprob function
    writeRaster(probbin, paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_binned_10_avgprob_", ascname, ".asc"), overwrite = TRUE)
    plot(probbin, png(paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_binned_10_avgprob_", ascname, ".png")), overwrite = TRUE)
    dev.off() # stops automatic saving of the plot to a png
  }
}
```

@@

  binaryavgstack <- stack(ascdepth)
  stackstathigh <- data.frame(matrix(ncol = 2, nrow = nlayers(binaryavgstack)))
  stackstathigh[ ,1] <- c(1:49)
  colnames(stackstathigh) <- c("asclayer", "prob_bin")

@@

```{r}
mthord <- c("mar",  "apr", "may", "jun", "jul", "aug", "sep", "oct", "nov", "dec")
cumst1 <- read.csv("../output/maxent/paper_plots/prob_by_depth/cellsperlayer.csv", header = TRUE)

@@

>>>>

#need to reclassify cells outside the mcp to NA for predictions
```{r}
outsidemcp <- shapefile("../data/env/landp/outside-mcp-wgs84.shp") #made in arcgis - in aea

ascdirs <- list.dirs("../data/env/ascii-original", full.names = FALSE, recursive = FALSE)

for (ad in 1:length(ascdirs)){
  timeslice <- ascdirs[ad]
  ascfiles <- list.files(paste0("../data/env/ascii-original/", timeslice), pattern = "\\.asc$", full.names = TRUE)
  for (file in 1:length(ascfiles)){
    ras<- raster(ascfiles[file])
    crs(ras) <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0 "
    ascname <- str_sub(ascfiles[file], start = 38)
    ras[outsidemcp] <- 500000
    ras[ras == 500000] <- NA
    writeRaster(ras, paste0("../data/env/asciitrim/", ascdirs[ad], "/", ascname), overwrite=TRUE)
  }
}

@@

```{r avg asc layers cloglog}
mthna <- "dec" #change me
depthlayers <- read.csv(paste0("../output/maxent/predictions/com-split/", mthna, "/cloglog_asclayerbydepth.csv"), header = TRUE)
p <- list.dirs("../output/maxent/models/test-comb", recursive = FALSE, full.names = FALSE)
modlist <- p[ grepl(mthna, p) ]
print(length(modlist)) #need this to modify code below
print(modlist) #need this to modify code below

for (x in 1:nrow(depthlayers)){
  asclay <- depthlayers[x, ]
  asclay <- asclay[!is.na(asclay)]
  asclay <- as.data.frame(rbind(asclay))
  asclay$V1 <- as.character(asclay$V1) #v1 just a number
  asclay$V2 <- as.character(asclay$V2) #v2 corresponds to depth
  asclay$V3 <- as.character(asclay$V3) #yr 1
  asclay$V4 <- as.character(asclay$V4) #yr 2
  asclay$V5 <- as.character(asclay$V5) #yr 3
  asclay$V6 <- as.character(asclay$V6) #yr 4
  asclay$V7 <- as.character(asclay$V7)
  asclay$V8 <- as.character(asclay$V8) #yr 6
  asclay$V9 <- as.character(asclay$V9)
  asclay$V10 <- as.character(asclay$V10) #yr 8
  asclay$V11 <- as.character(asclay$V11)
  asclay$V12 <- as.character(asclay$V12) #yr 10
  asclay$V13 <- as.character(asclay$V13)
  asclay$V14 <- as.character(asclay$V14) #yr 12
  asclay$V15 <- as.character(asclay$V15)
  asclay$V16 <- as.character(asclay$V16) #yr 14
  #asclay$V17<- as.character(asclay$V17)
  #asclay$V18 <- as.character(asclay$V18) #yr 16
  #asclay$V19 <- as.character(asclay$V19) #yr 17

@@

  asc1 <- raster(asclay$V3) #1
  asc2 <- raster(asclay$V4)
  asc3 <- raster(asclay$V5) #3
  asc4 <- raster(asclay$V6)
  asc5 <- raster(asclay$V7) #5
  asc6 <- raster(asclay$V8)
  asc7 <- raster(asclay$V9) #7
  asc8 <- raster(asclay$V10)
  asc9 <- raster(asclay$V11) #9
  asc10 <- raster(asclay$V12)
  asc11 <- raster(asclay$V13) #11
  asc12 <- raster(asclay$V14)
  asc13 <- raster(asclay$V15) #13
  asc14 <- raster(asclay$V16)
  #asc15 <- raster(asclay$V17) #15
 # asc16 <- raster(asclay$V18)
 # asc17 <- raster(asclay$V19)

  stkasc <- stack(asc1, asc2, asc3, asc4, asc5, asc6, asc7, asc8, asc9, asc10, asc11, asc12, asc13, asc14) #, asc15) #, asc16) #, asc2015)   asc1998, asc1999, asc2000, asc2001, asc2002, asc2003, asc2009

@@

file.rename(paste0("../output/maxent/predictions/com-split/", mthna, "/avg_cloglog_000120.asc"), paste0("../output/maxent/predictions/com-split", mthna, "/avg_cloglog_120.asc"))
file.rename(paste0("../output/maxent/predictions/com-split/", mthna, "/avg_cloglog_000120.png"), paste0("../output/maxent/predictions/com-split/", mthna, "/avg_cloglog_120.png"))
file.rename(paste0("../output/maxent/predictions/com-split/", mthna, "/avg_cloglog_041.18.asc"), paste0("../output/maxent/predictions/com-split/", mthna, "/avg_cloglog_41.18.asc"))
file.rename(paste0("../output/maxent/predictions/com-split/", mthna, "/avg_cloglog_041.18.png"), paste0("../output/maxent/predictions/com-split/", mthna, "/avg_cloglog_41.18.png"))
}
```

@@

```{r}
# outsidemcp <- shapefile("../data/env/landp/mcpout.shp") #made in arcgis
# wgsraster <- raster("../output/maxent/predictions/com-split/apr/cloglog_1998_04_0.50576.asc") #just chosen randomly to act as dummy file
# crs(wgsraster) <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0 "
# outsidemcp <- spTransform(outsidemcp, crs(wgsraster))

clogasc_list <- list.files(paste0("../output/maxent/predictions/com-split/mar"), pattern = "^avg_cloglog_.*.asc", full.names = TRUE) #just choose a random month to calculate cells
cumst <- data.frame(0, 0)
colnames(cumst) <- c("depth", "no_cells")
for (cum in 1:length(clogasc_list)){
  cumasc <- raster(clogasc_list[cum])
  ascname <- names(cumasc)
  cumst[cum, 1] <- str_sub(ascname, 13)
  #cumasc2 <- raster::mask(cumasc, outsidemcp, inverse = TRUE)
  ccnt <- freq(cumasc, useNA='no')
  ccnt <- sum(ccnt[ ,2])
  cumst[cum, 2] <- ccnt
}

@@

```{r bin probabilities}
#outsidemcp <- shapefile("../data/env/landp/mcpout.shp") #made in arcgis
mthord <- c("mar", "apr", "may", "jun", "jul", "aug", "sep", "oct", "nov", "dec")

for (m in 1:length(mthord)){
  mth <- mthord[m]
  clogasc_list <- list.files(paste0("../output/maxent/predictions/com-split/", mth), pattern = "^avg_cloglog.*.asc", full.names = TRUE)

@@

  for (cum in 1:length(clogasc_list)){
    cumasc <- raster(clogasc_list[cum])
    ascname <- names(cumasc)
    #cumasc <- mask(cumasc, outsidemcp, inverse = TRUE)
    probbin <- calc(cumasc, fun = binprob) #creates raster layer with cell values based on the binprob function
    writeRaster(probbin, paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_binned_1_avgprob_", ascname, ".asc"), overwrite = TRUE)
    plot(probbin, png(paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_binned_1_avgprob_", ascname, ".png")), overwrite = TRUE)
    dev.off() # stops automatic saving of the plot to a png
  }

@@

  for (cum in 1:length(clogasc_list)){
    cumasc <- raster(clogasc_list[cum])
    ascname <- names(cumasc)
    #cumasc <- mask(cumasc, outsidemcp, inverse = TRUE)
    probbin <- calc(cumasc, fun = binprob) #creates raster layer with cell values based on the binprob function
    writeRaster(probbin, paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_binned_2_avgprob_", ascname, ".asc"), overwrite = TRUE)
    plot(probbin, png(paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_binned_2_avgprob_", ascname, ".png")), overwrite = TRUE)
    dev.off() # stops automatic saving of the plot to a png
  }

@@

  for (cum in 1:length(clogasc_list)){
    cumasc <- raster(clogasc_list[cum])
    ascname <- names(cumasc)
    #cumasc <- mask(cumasc, outsidemcp, inverse = TRUE)
    probbin <- calc(cumasc, fun = binprob) #creates raster layer with cell values based on the binprob function
    writeRaster(probbin, paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_binned_3_avgprob_", ascname, ".asc"), overwrite = TRUE)
    plot(probbin, png(paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_binned_3_avgprob_", ascname, ".png")), overwrite = TRUE)
    dev.off() # stops automatic saving of the plot to a png
  }

@@

  for (cum in 1:length(clogasc_list)){
    cumasc <- raster(clogasc_list[cum])
    ascname <- names(cumasc)
    #cumasc <- mask(cumasc, outsidemcp, inverse = TRUE)
    probbin <- calc(cumasc, fun = binprob) #creates raster layer with cell values based on the binprob function
    writeRaster(probbin, paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_binned_4_avgprob_", ascname, ".asc"), overwrite = TRUE)
    plot(probbin, png(paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_binned_4_avgprob_", ascname, ".png")), overwrite = TRUE)
    dev.off() # stops automatic saving of the plot to a png
  }

@@

  for (cum in 1:length(clogasc_list)){
    cumasc <- raster(clogasc_list[cum])
    ascname <- names(cumasc)
    #cumasc <- mask(cumasc, outsidemcp, inverse = TRUE)
    probbin <- calc(cumasc, fun = binprob) #creates raster layer with cell values based on the binprob function
    writeRaster(probbin, paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_binned_5_avgprob_", ascname, ".asc"), overwrite = TRUE)
    plot(probbin, png(paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_binned_5_avgprob_", ascname, ".png")), overwrite = TRUE)
    dev.off() # stops automatic saving of the plot to a png
  }

@@

  for (cum in 1:length(clogasc_list)){
    cumasc <- raster(clogasc_list[cum])
    ascname <- names(cumasc)
    #cumasc <- mask(cumasc, outsidemcp, inverse = TRUE)
    probbin <- calc(cumasc, fun = binprob) #creates raster layer with cell values based on the binprob function
    writeRaster(probbin, paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_binned_6_avgprob_", ascname, ".asc"), overwrite = TRUE)
    plot(probbin, png(paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_binned_6_avgprob_", ascname, ".png")), overwrite = TRUE)
    dev.off() # stops automatic saving of the plot to a png
  }

@@

  for (cum in 1:length(clogasc_list)){
    cumasc <- raster(clogasc_list[cum])
    ascname <- names(cumasc)
    #cumasc <- mask(cumasc, outsidemcp, inverse = TRUE)
    probbin <- calc(cumasc, fun = binprob) #creates raster layer with cell values based on the binprob function
    writeRaster(probbin, paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_binned_7_avgprob_", ascname, ".asc"), overwrite = TRUE)
    plot(probbin, png(paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_binned_7_avgprob_", ascname, ".png")), overwrite = TRUE)
    dev.off() # stops automatic saving of the plot to a png
  }

@@

  for (cum in 1:length(clogasc_list)){
    cumasc <- raster(clogasc_list[cum])
    ascname <- names(cumasc)
    #cumasc <- mask(cumasc, outsidemcp, inverse = TRUE)
    probbin <- calc(cumasc, fun = binprob) #creates raster layer with cell values based on the binprob function
    writeRaster(probbin, paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_binned_8_avgprob_", ascname, ".asc"), overwrite = TRUE)
    plot(probbin, png(paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_binned_8_avgprob_", ascname, ".png")), overwrite = TRUE)
    dev.off() # stops automatic saving of the plot to a png
  }

@@

  for (cum in 1:length(clogasc_list)){
    cumasc <- raster(clogasc_list[cum])
    ascname <- names(cumasc)
    #cumasc <- mask(cumasc, outsidemcp, inverse = TRUE)
    probbin <- calc(cumasc, fun = binprob) #creates raster layer with cell values based on the binprob function
    writeRaster(probbin, paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_binned_9_avgprob_", ascname, ".asc"), overwrite = TRUE)
    plot(probbin, png(paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_binned_9_avgprob_", ascname, ".png")), overwrite = TRUE)
    dev.off() # stops automatic saving of the plot to a png
  }

@@

  for (cum in 1:length(clogasc_list)){
    cumasc <- raster(clogasc_list[cum])
    ascname <- names(cumasc)
   # cumasc <- mask(cumasc, outsidemcp, inverse = TRUE)
    probbin <- calc(cumasc, fun = binprob) #creates raster layer with cell values based on the binprob function
    writeRaster(probbin, paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_binned_10_avgprob_", ascname, ".asc"), overwrite = TRUE)
    plot(probbin, png(paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_binned_10_avgprob_", ascname, ".png")), overwrite = TRUE)
    dev.off() # stops automatic saving of the plot to a png
  }
}
```

@@

  binaryavgstack <- stack(ascdepth)
  stackstathigh <- data.frame(matrix(ncol = 2, nrow = nlayers(binaryavgstack)))
  stackstathigh[ ,1] <- c(1:47)
  colnames(stackstathigh) <- c("asclayer", "prob_bin")

@@

```{r}
mthord <- c("mar",  "apr", "may", "jun", "jul", "aug", "sep", "oct", "nov", "dec")
cumst1 <- read.csv("../output/maxent/paper_plots/cellsperlayer.csv", header = TRUE)

@@

GO FROM HERE

### 2020-01-25 src/testing_file.Rmd
moving forward... back to where i was

for (mth in 1:length(modlist)){
    mthna <- str_sub(modlist[mth], end = 3)
    yr <- str_sub(modlist[mth], start = 4)
    timeslice <- modlist[mth]
    mod <- readRDS(paste0("../output/maxent/models/test-comb/", timeslice, "/", timeslice, ".rda"))
    unlayer <- read.csv(paste0("../data/env/test-comb/asc_layerlist", mthna, ".csv"), header = TRUE) #if code doesnt work put back to unlayer_yr

>>>>

for (mth in 65:length(modlist)){
    mthna <- str_sub(modlist[mth], end = 3)
    yr <- str_sub(modlist[mth], start = 4)
    timeslice <- modlist[mth]
    mod <- readRDS(paste0("../output/maxent/models/test-comb/", timeslice, "/", timeslice, ".rda"))
    unlayer <- read.csv(paste0("../data/env/test-comb/asc_layerlist", mthna, ".csv"), header = TRUE) #if code doesnt work put back to unlayer_yr
